### 2013-02-27 thesis/chapter1/chapter1.tex
Added thesis as of 27 Feb

\documentclass[preprint2]{aastex}

\shorttitle{Kinematics \& Chemistry of Halo Substructures: The Vicinity of the VOD}
\shortauthors{Casey, Keller \& Da Costa}

\begin{document}

\title{Kinematics \& Chemistry of Halo Substructures: The Vicinity of the Virgo Over-Density}

\author{Andrew R. Casey, Stefan C. Keller and Gary Da Costa}
\affil{Research School of Astronomy \& Astrophysics,
	Australian National University, Mount Stromlo Observatory, via Cotter Rd, Weston, ACT 2611, Australia}

\begin{abstract}
We present observations obtained with the AAT's 2dF wide field spectrograph AAOmega of K-type stars located within a region of the sky which contains the Virgo Over-Density and the leading arm of the Sagittarius Stream.  On the basis of the resulting velocity histogram we isolate halo substructures in these overlapping regions including Sagittarius and previously discovered Virgo groups. Through comparisons with \textit{N}-body models of the Galaxy-Sagittarius interaction, we find a tri-axial dark matter halo is favoured and we exclude a prolate shape. This result is contradictory with other observations along the Sagittarius leading arm, which typically favour prolate models.  We have also uncovered K-giant members of Sagittarius that are notably more metal poor ($\langle[$Fe/H$]\rangle = -1.7\,\pm\,0.3$ dex) than previous studies. This suggests a significantly wider metallicity distribution exists in the Sagittarius Stream than formerly considered. We also present data on five carbon stars which were discovered in our sample.
\end{abstract}

\keywords{Galaxy: halo, structure --- Individual: Sagittarius, Virgo Stellar Stream --- Stars: carbon, K-giants}

\section{Introduction}
\label{sec:introduction}

The proportion of substructure recently uncovered in the Galaxy has highlighted the crucial involvement accretion has played in the formation of the Milky Way \citep[see][and references therein]{Helmi_2008}. Properties of these stellar structures allow us to probe the formation mechanisms and history of the Galaxy. Recent studies \citep{Carollo;et-al_2007, Carollo;et-al_2010} have suggested multiple evolutionary paths are required for galaxy formation to reconcile observational evidence, although this is a subject of ongoing debate \citep{Schoenrich;et-al_2011}. Regardless, the dissipation-less merging paradigm is widely accepted and consistent with favoured Cold Dark Matter ($\Lambda$CDM) cosmology models. Through the examination of ongoing accretion events in the Milky Way and fossils from previous mergers we can trace the evolution of the outer most regions of the Galaxy \citep[e.g.,][]{Helmi;White_2001}.

@@

After the Sgr stellar stream, the Virgo Over-Density (VOD) is arguably the next most significant substructure within our Galaxy. The first over-density in the vicinity of the VOD was observed as a group of RR Lyrae stars by the QUEST survey \citep{Vivas;et-al_2001}. The collaboration later named this the ``$12\fh4$ clump'' \citep{Zinn;et-al_2004}. The broad nature of the VOD was later uncovered from the SDSS catalogue as a diffuse over-density of main-sequence turnoff stars centered at $r_\odot \sim18$ kpc \citep[which ][dubbed as S297+63-20.5]{Newberg;et-al_2002}. The nomenclature on the substructure names within this region is varied, however in this paper when referring to the VOD we are discussing the spatial over-density of stars within the region, separate from any detected co-moving groups.

The difficulty arises in accurately distinguishing the VOD as there are multiple substructures along this line-of-sight. \citet{Duffau;et-al_2006} took observations of BHB and RR Lyrae within the ``$12\fh4$ clump'' and found a common velocity of $V_{GSR} = 99.8$ km s$^{-1}$ with $\sigma_{v} = 17.3$ km s$^{-1}$. It should be noted that the dispersion in kinematics measured by \citet{Duffau;et-al_2006} is essentially their velocity precision, so the substructure may possess a much smaller kinematic dispersion. This co-moving group was coined the Virgo Stellar Stream (VSS) to differentiate it from the broad spatial over-density. This distinction from the VOD was somewhat strengthened with new distance measurements which placed the VOD centroid at $r_\odot = 16$ kpc \citep{Juric;et-al_2008, Keller_2010}, and the VSS 3 kpc further away \citep{Duffau;et-al_2006}. Although, when considered in the light of systematic and observational uncertainties, this is of marginal significance. Additionally, \citet{Juric;et-al_2008} suggests the VOD may extend between $r_\odot = 6$ to 20 kpc, which further complicates the matter of distance separation.

@@

Target selection methodology is outlined in the next section which is followed with details regarding the observations. Techniques used to separate K-giants from dwarfs are discussed in \S\ref{sec:dwarf-giant-separation}, and our analysis procedure for kinematics (\S\ref{sec:kinematics}) and metallicities (\S\ref{sec:metallicities}) follows. A discussion of substructures is outlined in \S\ref{sec:discussion}, and in \S\ref{sec:carbon-stars} we report the carbon stars discovered in our sample. In \S\ref{sec:conclusions} we conclude with some final remarks and critical interpretations.

\section{Target Selection}
\label{sec:target-selection}

When the presence of a stellar substructure is uncovered, K-giants provide excellent candidates for spectroscopic follow-up. They allow for precise radial velocities and chemical abundances. In order to specifically target K-giants we have chosen candidates within the color selection box shown in Figure \ref{fig:cmd-target-selection}, taken from the SDSS DR7 catalogue. This selection box favors a metal-poor population at Sgr stream-like distances ($\sim40$ kpc) but will also contain similarly metal-poor stars at VOD/VSS distances ($\sim20$ kpc) without being significantly biased. Field dwarfs are expected to contaminate the sample due to their similarity in colors. Although K-dwarfs are difficult to distinguish photometrically we can spectroscopically separate these through the equivalent width (EW) of the  gravity-sensitive Mg I triplet lines at 5167.3, 5172.7, and 5183.6 \AA\ (see \S\ref{sec:dwarf-giant-separation}).

\begin{figure}[h]
	\includegraphics[width=\columnwidth]{./cmd.eps}
	\caption{CMD of our observed regions from SDSS DR7, overlaid with the color selection criterion used to target K-giants. Appropriate Dartmouth isochrones \citep{Dotter;et-al_2008} are shown for Sgr debris at a distance of $r_\odot =40$ kpc \citep{Belokurov;et-al_2006}}
	\label{fig:cmd-target-selection}
\end{figure}

\section{Observations}
\label{sec:observations}

@@

% NOTE TO THE EDITOR - This table ought to be in a single column.

\begin{deluxetable}{cccc}
\tablecolumns{1}
\tablewidth{0pt}
\tabletypesize{\scriptsize}
\tablecaption{Observed fields\label{tab:observations}}
\tablehead{
	\colhead{Field} &
	\colhead{$\alpha$-center} &
	\colhead{$\delta$-center} &
	\colhead{Field} \\ 
	& (J2000.0) & (J2000.0) & Configurations
}
\startdata
A & 12 00 00 & $+00$ 00 00 & 1 \\ 
B & 12 20 00 & $-01$ 00 00 & 2 \\ 
C & 12 40 00 & $-02$ 00 00 & 3 \\ 
D & 12 56 00 & $-02$ 42 00 & 6 \\ 
\enddata
\end{deluxetable}

@@

\section{Dwarf / Giant separation}
\label{sec:dwarf-giant-separation}

@@

\begin{figure}[h]
	\includegraphics[width=\columnwidth]{./dwarfgiant.eps}
	\caption{The sum of the Mg I triplet EWs for observations and synthetic spectra shown against the Sloan $g\,-\,i$ color. Synthetic spectra are shown for $\log{g} = 2$ ($\bigtriangledown$) and $\log{g} = 4.5$ ($\bigtriangleup$), and points are colored by metallicity. Our dwarf/giant separation line is shown (solid). }
	\label{fig:dwarf-giant-separation}
\end{figure}

@@

\section{Radial Velocities}
\label{sec:kinematics}

@@

\section{Metallicities}
\label{sec:metallicities}

@@

Using this calibration our globular cluster standard stars (with known $V_{HB}$ magnitudes) have metallicities that match well with the \citet{Harris_1996} catalogue (2011 edition). Only K-giants within the valid calibration range ($0 > V-V_{HB} > -3$) were considered for metallicities. We assume that we have two dominant substructures present in our observations; the leading arm of Sgr and the Virgo Over-Density (see \S\ref{sec:substructure-identification}). The Sgr stream dominates our negative $V_{GSR}$ population, and our positive kinematic space primarily comprises VOD and VSS members. As such we have separated our population at $V_{GSR} = 0$ km s$^{-1}$ into two samples with assumed $V_{HB}$ magnitudes. Although this introduces a (known) systemic effect, it is a required assumption to estimate the metallicity distribution of each population.

@@

We have assumed distances to these stars by interpolating their position along a cubic spline fitted to published distances \citep{Siegel;et-al_2007}. Recent distance measurements of the stream by \citet{Ruhland;et-al_2011} match the stream distances used here within the uncertainties. The horizontal branch magnitude $V_{HB}$ is calculated using this assumed distance and the known luminosity of RR Lyrae stars \citep[$M_V = +0.69;$][]{Tsujimoto;et-al_1998}. Typical $V_{HB}$ magnitude derived for the Sgr members is $18.7$, corresponding to a distance of $\sim{}41$ kpc. Reddening is accounted for using the \citet{Schlegel;Finkbeiner;Davis_1998} maps with \citet{Schlafly;Finkbeiner_2011} corrections as described in \S\ref{sec:dwarf-giant-separation}. Uncertainties in distance are not interpolated; they are taken as the largest published uncertainty of the closest neighbouring data points, and this is propagated through to our reported metallicity uncertainties. The kinematics and metallicities derived for our giant sample are discussed in the following section.

\section{Discussion}
\label{sec:discussion}

	\subsection{Substructure Identification}
	\label{sec:substructure-identification}

@@

	\begin{figure}[h!]
		\includegraphics[width=\columnwidth]{./velocity_halo.eps}
		\caption{Generalised histogram of $V_{GSR}$ for our 178 K-type giants, highlighting the substructure present. The Gaussian represents the halo contribution; it is normalised such that the integral equals the number of observed stars excluding those outside a 2.5-$\sigma$ excess. Significant ($>3\sigma$) kinematic deviations from the smooth distribution are appropriately grouped and labelled.}
		\label{fig:velocity-histogram}
	\end{figure}

		\begin{figure*}[t!]
		\includegraphics[width=\textwidth]{./monte_carlo.eps}
		\caption{The observed data for the 178 giant star sample (left panel). Monte-Carlo simulation results illustrating the number of times simulations could reproduce our observed data in the equivalent multi-dimensional bin (right panel). Significant features discussed in the text are labelled.}
		\label{fig:monte-carlo}
	\end{figure*}

@@

	 Substructure becomes statistically significant when the observed grid blocks are rarely replicated in Monte-Carlo simulations. Specifically, the number of members in Feature A was never reproduced in some grid bins. This feature is well in excess of the halo and has a wide spread in kinematics. \citet{Chou;et-al_2007} mapped the Sgr debris across the sky using K/M-giants and found galactocentric velocity signatures between $-205$ km s$^{-1}$ to $-31$ km s$^{-1}$ in this region. As such we attribute this wide, significant kinematic peak as the leading arm of the Sgr tidal tail. Feature A is discussed in the next section. Another feature where grid blocks were never reproduced in our simulations was Feature C. This feature may also be attributed to Sgr debris and is discussed further in \S\ref{sec:feature-c}.

	 The clump of stars in the velocity bin centered on $V_{GSR} \approx 130$ km s$^{-1}$ and [Fe/H] $\approx -2$ was replicated only $\sim1$\% in 10,000 simulations. We attribute these stars to the Virgo Stellar Stream, as they are coincident in spatial position, velocity, and metallicity with previously reported values of the VSS obtained by F turnoff/BHB stars \citep{Newberg;et-al_2007} and RR Lyrae stars \citep{Prior;et-al_2009a}. Feature B is discussed in \S\ref{sec:the-vss}.

	\begin{figure*}[t!]
		\includegraphics[width=\textwidth]{./adapted_belokurov_2006.eps}
		\caption{Observed fields are outlined upon a panoramic view of the Sgr stream, to demonstrate our field locations in context with the Sgr stream. This plot is an adaptation of Figure 2 in \citet{Belokurov;et-al_2006}, which uses the 2MASS M-giant sample of \citet{Majewski;et-al_2003}.}
		\label{fig:sgr-field-of-streams}
	\end{figure*}

	\subsection{Feature A \--- Sagittarius Debris}
	\label{sec:sgr-debris}

@@

	\begin{figure}[t!]
		\includegraphics[width=\columnwidth]{./law_spatial.eps}
		\caption{Our fields and observed bounds are shown with the simulated particles from multiple \textit{N}-body simulations by LJM05 and LM10. These particles are distance restricted (up to 60 kpc), and color-coded by their peri-centric passage (yellow; most recent passage, red; previous passage, blue; oldest observable passage).}
		\label{fig:law-spatial}
	\end{figure}

@@

	\begin{figure*}[t!]
		\includegraphics[width=\textwidth]{./sgr_velocities.eps}
		\caption{A generalised histogram (left) of the galactocentric rest frame velocities in our sample (dotted line) compared to the velocities (solid line) from the \textit{N}-body models of LJM05, LM10 of particles within the same spatial coverage and distance range (up to $r_\odot \sim 60$ kpc) of our observed sample. Heliocentric distances for particles used to generate each velocity histogram are shown on the right. Particles are marked by their peri-centric passage. A plus ($+$) denotes debris from the current peri-centric passage by Sgr, circles ($\circ$) mark the previous passage, and squares ($\square$) represent debris from two previous passages. The prolate model from LJM05 is not considered in this plot (see text).}
		\label{fig:law-vel-compare}
	\end{figure*}

@@

	\subsubsection{A Metal-Poor Population Uncovered in Sagittarius Debris}
	\label{sec:sgr-metal-poor}

@@

	\begin{figure}[h]
		\includegraphics[width=\columnwidth]{./sgr_feh_hist.eps}
		\caption{Metallicity histograms for K-giant members in our negative galactocentric velocity sample, which is largely populated by Sgr debris from the Northern leading arm.}
		\label{fig:sgr-metallicity-hist}
	\end{figure}

@@

	\subsection{Feature B \--- The Virgo Stellar Stream}
	\label{sec:the-vss}

@@

	\subsection{Feature C \--- Sagittarius debris?}
	\label{sec:feature-c}

@@

\section{Carbon Stars}
\label{sec:carbon-stars}

@@

\begin{figure}[h!]
	\includegraphics[width=\columnwidth]{./carbon_stars.eps}
	\caption{Sloan \textit{u \--- g} and \textit{g \--- r} colors for our carbon stars, and the identified carbon stars and classifications by \citet{Downes;et-al_2004}. Carbon stars identified in this work have been shaded for clarity.}
	\label{fig:carbon-sdss}
\end{figure}

@@

\begin{deluxetable}{cccccccccccc}
\tablewidth{0pt}
\tabletypesize{\scriptsize}
\tablecaption{Properties of carbon stars found in our sample \label{tb:carbon-stars}}
\tablehead{
	\colhead{SDSS Name J+\tablenotemark{a}} & 
	\colhead{$M_g$} &
	\colhead{\it{u-g}} &
	\colhead{\it{g-r}} &
	\colhead{\it{r-i}} &
	\colhead{\it{i-z}} &
	\colhead{\it{H-K}} &
	\colhead{\it{J-H}} &
	\colhead{$\mu_{\alpha\cos{\delta}}\tablenotemark{c}$} &
	\colhead{$\mu_\delta\tablenotemark{c}$} &
	\colhead{$V_{GSR}$} & 
	\colhead{Likely} \\
	& & & & & & & & (mas yr$^{-1}$) & (mas yr$^{-1}$) & (km s$^{-1}$) & dwarf?
}

\startdata
121740.94-001839.5 & 18.66 & 1.10 & 0.54 & 0.16 & 0.05 & ...\tablenotemark{b}& ...\tablenotemark{b} & \phn$-3.0 \pm 5.4$  & $-18.0 \pm 5.4$\phn & $\phn-71 \pm 34$ & Yes\\
121853.18-004628.4 & 17.71 & 1.67 & 0.73 & 0.22 & 0.11 & \phd0.24 & 0.36 &  \phn$-3.7 \pm 4.5$ & $-0.5 \pm 4.5$ & $+176 \pm 9$ & - \\
122053.71-011709.5 & 17.65 & 1.79 & 0.80 & 0.26 & 0.13 & \phd0.16 & 0.56 &  \phn$-7.3 \pm 4.3$ & $-3.9 \pm 4.3$ & $\phn+31 \pm 11$ & - \\
125410.80-032744.0 & 18.59 & 1.43 & 0.64 & 0.22 & 0.05 & \phd0.56 & 0.32 &$-21.1 \pm 5.0 $ & $-7.7 \pm 5.0$ & $\phn-41 \pm 9\phn$ & Yes \\ 
125416.52-031437.6 & 16.85 & 1.72 & 0.73 & 0.25 & 0.11 & -0.11 & 0.50 & $-19.8 \pm 4.2$ & \phd\phn$8.7 \pm 4.2$& $\phn+15 \pm 4\phn$ & Yes \\
\enddata
\tablenotetext{a}{To keep with convention, positional information has been truncated. Full information available through the SDSS archive.}
\tablenotetext{b}{No \textit{JHK} photometry is available for this object as it is fainter than the 2MASS survey limit.}
\tablenotetext{c}{Proper motions taken from the PPMXL Catalog \citep{Roser;et-al_2010}.}
\end{deluxetable}

@@

\section{Conclusions}
\label{sec:conclusions}

@@

\section{Acknowledgements}
ARC acknowledges the financial support through the Australian Research Council Laureate Fellowship 0992131. SK and GDaC acknowledge the financial support from the Australian Research Council through Discovery Program DP0878137.

This publication makes use of data products from the Two Micron All Sky Survey, which is a joint project of the University of Massachusetts and the Infrared Processing and Analysis Center/California Institute of Technology, funded by the National Aeronautics and Space Administration and the National Science Foundation.

Funding for the SDSS and SDSS-II has been provided by the Alfred P. Sloan Foundation, the Participating Institutions, the National Science Foundation, the U.S. Department of Energy, the National Aeronautics and Space Administration, the Japanese Monbukagakusho, the Max Planck Society, and the Higher Education Funding Council for England. The SDSS Web Site is http://www.sdss.org/.

The SDSS is managed by the Astrophysical Research Consortium for the Participating Institutions. The Participating Institutions are the American Museum of Natural History, Astrophysical Institute Potsdam, University of Basel, University of Cambridge, Case Western Reserve University, University of Chicago, Drexel University, Fermilab, the Institute for Advanced Study, the Japan Participation Group, Johns Hopkins University, the Joint Institute for Nuclear Astrophysics, the Kavli Institute for Particle Astrophysics and Cosmology, the Korean Scientist Group, the Chinese Academy of Sciences (LAMOST), Los Alamos National Laboratory, the Max-Planck-Institute for Astronomy (MPIA), the Max-Planck-Institute for Astrophysics (MPA), New Mexico State University, Ohio State University, University of Pittsburgh, University of Portsmouth, Princeton University, the United States Naval Observatory, and the University of Washington.
\bibliographystyle{apj}
\bibliography{bibliography}

\end{document}

>>>>

\chapter{The Kinematics \& Chemistry of Halo Substructures in the Vicinity of the Virgo Over-Density}

% you can put a brief note at the top of your chapters using '\previouslypublished{}'. For example, to give a reference to the paper this chapter is based on, or to point out that it has been submitted to a journal.

\previouslypublished{Parts of this chapter have been previously published as \href{http://adsabs.harvard.edu/abs/2012AJ....143...88C}{`Kinematics \& Chemistry of Halo Substructures: The Vicinity of the Virgo Over-Density', {Casey}, A.~R., {Keller}, S.~C., {Da Costa}, G., 2012, AJ, 143, 88C}. The work is presented here in expanded and updated form.}

\section{Introduction}
The proportion of substructure recently uncovered in the Galaxy has highlighted the crucial involvement accretion has played in the formation of the Milky Way \citep[see][and references therein]{Helmi_2008}. Properties of these stellar structures allow us to probe the formation mechanisms and history of the Galaxy. Recent studies \citep{Carollo;et-al_2007, Carollo;et-al_2010} have suggested multiple evolutionary paths are required for galaxy formation to reconcile observational evidence, although this is a subject of ongoing debate \citep{Schoenrich;et-al_2011}. Regardless, the dissipation-less merging paradigm is widely accepted and consistent with favoured Cold Dark Matter ($\Lambda$CDM) cosmology models. Through the examination of ongoing accretion events in the Milky Way and fossils from previous mergers we can trace the evolution of the outer most regions of the Galaxy \citep[e.g.,][]{Helmi;White_2001}.

@@

After the Sgr stellar stream, the Virgo Over-Density (VOD) is arguably the next most significant substructure within our Galaxy. The first over-density in the vicinity of the VOD was observed as a group of RR Lyrae stars by the QUEST survey \citep{Vivas;et-al_2001}. The collaboration later named this the ``$12{\mbox{$.\!\!^{\mathrm h}$}}4$ clump'' \citep{Zinn;et-al_2004}. The broad nature of the VOD was later uncovered from the SDSS catalogue as a diffuse over-density of main-sequence turnoff stars centered at $r_\odot \sim18$ kpc \citep[which ][dubbed as S297+63-20.5]{Newberg;et-al_2002}. The nomenclature on the substructure names within this region is varied, however in this paper when referring to the VOD we are discussing the spatial over-density of stars within the region, separate from any detected co-moving groups.

The difficulty arises in accurately distinguishing the VOD as there are multiple substructures along this line-of-sight. \citet{Duffau;et-al_2006} took observations of BHB and RR Lyrae within the ``$12{\mbox{$.\!\!^{\mathrm h}$}}4$ clump'' and found a common velocity of $V_{GSR} = 99.8$ km s$^{-1}$ with $\sigma_{v} = 17.3$ km s$^{-1}$. It should be noted that the dispersion in kinematics measured by \citet{Duffau;et-al_2006} is essentially their velocity precision, so the substructure may possess a much smaller kinematic dispersion. This co-moving group was coined the Virgo Stellar Stream (VSS) to differentiate it from the broad spatial over-density. This distinction from the VOD was somewhat strengthened with new distance measurements which placed the VOD centroid at $r_\odot = 16$ kpc \citep{Juric;et-al_2008, Keller_2010}, and the VSS 3 kpc further away \citep{Duffau;et-al_2006}. Although, when considered in the light of systematic and observational uncertainties, this is of marginal significance. Additionally, \citet{Juric;et-al_2008} suggests the VOD may extend between $r_\odot = 6$ to 20 kpc, which further complicates the matter of distance separation.

@@

Target selection methodology is outlined in the next section which is followed with details regarding the observations. Techniques used to separate K-giants from dwarfs are discussed in \S\ref{sec:ch1-dwarf-giant-separation}, and our analysis procedure for kinematics (\S\ref{sec:ch1-kinematics}) and metallicities (\S\ref{sec:ch1-metallicities}) follows. A discussion of substructures is outlined in \S\ref{sec:ch1-discussion}, and in \S\ref{sec:ch1-carbon-stars} we report the carbon stars discovered in our sample. In \S\ref{sec:ch1-conclusions} we conclude with some final remarks and critical interpretations.

\section{Target Selection}
\label{sec:ch1-target-selection}

When the presence of a stellar substructure is uncovered, K-giants provide excellent candidates for spectroscopic follow-up. They allow for precise radial velocities and chemical abundances. In order to specifically target K-giants we have chosen candidates within the color selection box shown in Figure \ref{fig:cmd-target-selection}, taken from the SDSS DR7 catalogue. This selection box favors a metal-poor population at Sgr stream-like distances ($\sim40$ kpc) but will also contain similarly metal-poor stars at VOD/VSS distances ($\sim20$ kpc) without being significantly biased. Field dwarfs are expected to contaminate the sample due to their similarity in colors. Although K-dwarfs are difficult to distinguish photometrically we can spectroscopically separate these through the equivalent width (EW) of the  gravity-sensitive Mg I triplet lines at 5167.3, 5172.7, and 5183.6 \AA\ (see \S\ref{sec:ch1-dwarf-giant-separation}).

\begin{figure}[h]
	\includegraphics[width=\columnwidth]{chapter1/cmd.pdf}
	\caption{CMD of our observed regions from SDSS DR7, overlaid with the color selection criterion used to target K-giants. Appropriate Dartmouth isochrones \citep{Dotter;et-al_2008} are shown for Sgr debris at a distance of $r_\odot =40$ kpc \citep{Belokurov;et-al_2006}}
	\label{fig:cmd-target-selection}
\end{figure}

\section{AAT Observations with AAOmega}
\label{sec:ch1-observations}

@@

@@

\section{Dwarf / Giant separation}
\label{sec:ch1-dwarf-giant-separation}

@@

\begin{figure}[h]
	\includegraphics[width=\columnwidth]{chapter1/dwarfgiant.pdf}
	\caption{The sum of the Mg I triplet EWs for observations and synthetic spectra shown against the Sloan $g\,-\,i$ color. Synthetic spectra are shown for $\log{g} = 2$ ($\bigtriangledown$) and $\log{g} = 4.5$ ($\bigtriangleup$), and points are colored by metallicity. Our dwarf/giant separation line is shown (solid). }
	\label{fig:dwarf-giant-separation}
\end{figure}

@@

\section{Radial Velocities}
\label{sec:ch1-kinematics}

@@

\section{Metallicities}
\label{sec:ch1-metallicities}

@@

Using this calibration our globular cluster standard stars (with known $V_{HB}$ magnitudes) have metallicities that match well with the \citet{Harris_1996} catalogue (2011 edition). Only K-giants within the valid calibration range ($0 > V-V_{HB} > -3$) were considered for metallicities. We assume that we have two dominant substructures present in our observations; the leading arm of Sgr and the Virgo Over-Density (see \S\ref{sec:ch1-substructure-identification}). The Sgr stream dominates our negative $V_{GSR}$ population, and our positive kinematic space primarily comprises VOD and VSS members. As such we have separated our population at $V_{GSR} = 0$ km s$^{-1}$ into two samples with assumed $V_{HB}$ magnitudes. Although this introduces a (known) systemic effect, it is a required assumption to estimate the metallicity distribution of each population.

@@

We have assumed distances to these stars by interpolating their position along a cubic spline fitted to published distances \citep{Siegel;et-al_2007}. Recent distance measurements of the stream by \citet{Ruhland;et-al_2011} match the stream distances used here within the uncertainties. The horizontal branch magnitude $V_{HB}$ is calculated using this assumed distance and the known luminosity of RR Lyrae stars \citep[$M_V = +0.69;$][]{Tsujimoto;et-al_1998}. Typical $V_{HB}$ magnitude derived for the Sgr members is $18.7$, corresponding to a distance of $\sim{}41$ kpc. Reddening is accounted for using the \citet{Schlegel;Finkbeiner;Davis_1998} maps with \citet{Schlafly;Finkbeiner_2011} corrections as described in \S\ref{sec:ch1-dwarf-giant-separation}. Uncertainties in distance are not interpolated; they are taken as the largest published uncertainty of the closest neighbouring data points, and this is propagated through to our reported metallicity uncertainties. The kinematics and metallicities derived for our giant sample are discussed in the following section.

\section{Discussion}
\label{sec:ch1-discussion}

	\subsection{Substructure Identification}
	\label{sec:ch1-substructure-identification}

@@

	\begin{figure}[h!]
		\includegraphics[width=\columnwidth]{chapter1/velocity_halo.pdf}
		\caption{Generalised histogram of $V_{GSR}$ for our 178 K-type giants, highlighting the substructure present. The Gaussian represents the halo contribution; it is normalised such that the integral equals the number of observed stars excluding those outside a 2.5-$\sigma$ excess. Significant ($>3\sigma$) kinematic deviations from the smooth distribution are appropriately grouped and labelled.}
		\label{fig:velocity-histogram}
	\end{figure}

%\begin{figure}[h]
%		\includegraphics[width=\columnwidth]{chapter1/monte_carlo.pdf}
%		\caption{The observed data for the 178 giant star sample (left panel). Monte-Carlo simulation results illustrating the number of times simulations could reproduce our observed data in the equivalent multi-dimensional bin (right panel). Significant features discussed in the text are labelled.}
%		\label{fig:monte-carlo}
%	\end{figure}

@@

	 Substructure becomes statistically significant when the observed grid blocks are rarely replicated in Monte-Carlo simulations. Specifically, the number of members in Feature A was never reproduced in some grid bins. This feature is well in excess of the halo and has a wide spread in kinematics. \citet{Chou;et-al_2007} mapped the Sgr debris across the sky using K/M-giants and found galactocentric velocity signatures between $-205$ km s$^{-1}$ to $-31$ km s$^{-1}$ in this region. As such we attribute this wide, significant kinematic peak as the leading arm of the Sgr tidal tail. Feature A is discussed in the next section. Another feature where grid blocks were never reproduced in our simulations was Feature C. This feature may also be attributed to Sgr debris and is discussed further in \S\ref{sec:ch1-feature-c}.

	 The clump of stars in the velocity bin centered on $V_{GSR} \approx 130$ km s$^{-1}$ and [Fe/H] $\approx -2$ was replicated only $\sim1$\% in 10,000 simulations. We attribute these stars to the Virgo Stellar Stream, as they are coincident in spatial position, velocity, and metallicity with previously reported values of the VSS obtained by F turnoff/BHB stars \citep{Newberg;et-al_2007} and RR Lyrae stars \citep{Prior;et-al_2009a}. Feature B is discussed in \S\ref{sec:ch1-the-vss}.

%	\begin{figure}
%		\includegraphics[width=\columnwidth]{chapter1/adapted_belokurov_2006.pdf}
%		\caption{Observed fields are outlined upon a panoramic view of the Sgr stream, to demonstrate our field locations in context with the Sgr stream. This plot is an adaptation of Figure 2 in \citet{Belokurov;et-al_2006}, which uses the 2MASS M-giant sample of \citet{Majewski;et-al_2003}.}
%		\label{fig:sgr-field-of-streams}
%\end{figure}

	\subsection{Feature A \--- Sagittarius Debris}
	\label{sec:ch1-sgr-debris}

@@

	\begin{figure}[t!]
		\includegraphics[width=\columnwidth]{chapter1/law_spatial.pdf}
		\caption{Our fields and observed bounds are shown with the simulated particles from multiple \textit{N}-body simulations by LJM05 and LM10. These particles are distance restricted (up to 60 kpc), and color-coded by their peri-centric passage (yellow; most recent passage, red; previous passage, blue; oldest observable passage).}
		\label{fig:law-spatial}
	\end{figure}

@@

	\begin{figure*}[t!]
		\includegraphics[width=\textwidth]{chapter1/sgr_velocities.pdf}
		\caption{A generalised histogram (left) of the galactocentric rest frame velocities in our sample (dotted line) compared to the velocities (solid line) from the \textit{N}-body models of LJM05, LM10 of particles within the same spatial coverage and distance range (up to $r_\odot \sim 60$ kpc) of our observed sample. Heliocentric distances for particles used to generate each velocity histogram are shown on the right. Particles are marked by their peri-centric passage. A plus ($+$) denotes debris from the current peri-centric passage by Sgr, circles ($\circ$) mark the previous passage, and squares ($\square$) represent debris from two previous passages. The prolate model from LJM05 is not considered in this plot (see text).}
		\label{fig:law-vel-compare}
	\end{figure*}

@@

	\subsubsection{A Metal-Poor Population Uncovered in Sagittarius Debris}
	\label{sec:ch1-sgr-metal-poor}

@@

	\begin{figure}[h]
		\includegraphics[width=\columnwidth]{chapter1/sgr_feh_hist.pdf}
		\caption{Metallicity histograms for K-giant members in our negative galactocentric velocity sample, which is largely populated by Sgr debris from the Northern leading arm.}
		\label{fig:sgr-metallicity-hist}
	\end{figure}

@@

	\subsection{Feature B \--- The Virgo Stellar Stream}
	\label{sec:ch1-the-vss}

@@

	\subsection{Feature C \--- Sagittarius debris?}
	\label{sec:ch1-feature-c}

@@

\section{Carbon Stars}
\label{sec:ch1-carbon-stars}

@@

\begin{figure}[h!]
	\includegraphics[width=\columnwidth]{chapter1/carbon_stars.pdf}
	\caption{Sloan \textit{u \--- g} and \textit{g \--- r} colors for our carbon stars, and the identified carbon stars and classifications by \citet{Downes;et-al_2004}. Carbon stars identified in this work have been shaded for clarity.}
	\label{fig:carbon-sdss}
\end{figure}

@@

%\begin{deluxetable}{cccccccccccc}
%\tablewidth{0pt}
%\tabletypesize{\scriptsize}
%\tablecaption{Properties of carbon stars found in our sample \label{tb:carbon-stars}}
%\tablehead{
%	\colhead{SDSS Name J+\tablenotemark{a}} & 
%	\colhead{$M_g$} &
%	\colhead{\it{u-g}} &
%	\colhead{\it{g-r}} &
%	\colhead{\it{r-i}} &
%	\colhead{\it{i-z}} &
%	\colhead{\it{H-K}} &
%	\colhead{\it{J-H}} &
%	\colhead{$\mu_{\alpha\cos{\delta}}\tablenotemark{c}$} &
%	\colhead{$\mu_\delta\tablenotemark{c}$} &
%	\colhead{$V_{GSR}$} & 
%	\colhead{Likely} \\
%	& & & & & & & & (mas yr$^{-1}$) & (mas yr$^{-1}$) & (km s$^{-1}$) & dwarf?
%}

%\startdata
%121740.94-001839.5 & 18.66 & 1.10 & 0.54 & 0.16 & 0.05 & ...\tablenotemark{b}& ...\tablenotemark{b} & \phn$-3.0 \pm 5.4$  & $-18.0 \pm 5.4$\phn & $\phn-71 \pm 34$ & Yes\\
%121853.18-004628.4 & 17.71 & 1.67 & 0.73 & 0.22 & 0.11 & \phd0.24 & 0.36 &  \phn$-3.7 \pm 4.5$ & $-0.5 \pm 4.5$ & $+176 \pm 9$ & - \\
%122053.71-011709.5 & 17.65 & 1.79 & 0.80 & 0.26 & 0.13 & \phd0.16 & 0.56 &  \phn$-7.3 \pm 4.3$ & $-3.9 \pm 4.3$ & $\phn+31 \pm 11$ & - \\
%125410.80-032744.0 & 18.59 & 1.43 & 0.64 & 0.22 & 0.05 & \phd0.56 & 0.32 &$-21.1 \pm 5.0 $ & $-7.7 \pm 5.0$ & $\phn-41 \pm 9\phn$ & Yes \\ 
%125416.52-031437.6 & 16.85 & 1.72 & 0.73 & 0.25 & 0.11 & -0.11 & 0.50 & $-19.8 \pm 4.2$ & \phd\phn$8.7 \pm 4.2$& $\phn+15 \pm 4\phn$ & Yes \\
%\enddata
%\tablenotetext{a}{To keep with convention, positional information has been truncated. Full information available through the SDSS archive.}
%\tablenotetext{b}{No \textit{JHK} photometry is available for this object as it is fainter than the 2MASS survey limit.}
%\tablenotetext{c}{Proper motions taken from the PPMXL Catalog \citep{Roser;et-al_2010}.}
%\end{deluxetable}

@@

\section{Conclusions}
\label{sec:ch1-conclusions}

@@
